State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

 \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{f-}

@@

\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1|t}^{b-}$ similar to the forward step and compute

@@

 \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1|t}^{b-}

@@

\end{algorithmic}
\end{algorithm}
\section{Results}
The neural field model was used to the generate data for state and parameter estimation. All parameters for the model are given in Table~\ref{}. An example of the simulated field can be seen in Figure~\ref{}~A. The Figure demonstrates the experimental design where the sensors were placed in the centre of the field. This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions. Figure~\ref{}~B. shows example data from the sensors of the model, and Figure~\ref{}~C. shows the power spectral density of on of the simulated time-series. The PSD shows the typical $1/f$ characteristics of intracranial EEG.
% \begin{figure}
% 	\centering
% 		\includegraphics[scale=1]{file.eps}
% 	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the width ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
% 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
% \end{figure}

>>>>

 \hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-}

@@

\State Calculate a new set of  sigma points, $\mathcal X_{i,t+1}^{b-}$ similar to the forward step and compute

@@

 \hat{\mathbf x}_{t+1}^{b-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{b-}

@@

\State compute the smoother gain $\mathbf S_t$, the smoothed state $\hat{\mathbf x}_t^b $ and the covariance $\mathbf P_{t}^{b} $
\mathbf S_t=\mathbf M_{t +1}\left[ \mathbf P_{t +1}^{b-}\right] ^{-1}
 \hat{\mathbf x}_t^b=\hat{\mathbf x}_t^f+\mathbf S_t\left[\hat{\mathbf x}_{t+1}^{b}-\hat{\mathbf x}_{t+1}^{b-}\right] 
 \mathbf P_{t}^{b}=\mathbf P_{t}^{f}+\mathbf S_t\left[\mathbf P_{t+1}^{b}-\mathbf P_{t+1}^{b-} \right]\mathbf S_t^\top 

\end{algorithmic}
\end{algorithm}
\section{Results}
The neural field model was used to the generate data for state and parameter estimation. All parameters for the model are given in Table~\ref{}. An example of the simulated field can be seen in Figure~\ref{}~A. The Figure demonstrates the experimental design where the sensors were placed in the centre of the field. This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions. Figure~\ref{}~B. shows example data from the sensors of the model, and Figure~\ref{}~C. shows the power spectral density of on of the simulated time-series. The PSD shows the typical $1/f$ characteristics of intracranial EEG.
% \begin{figure}
% 	\centering
% 		\includegraphics[scale=1]{file.eps}
% 	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the width ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
% 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
% \end{figure}
